An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Forgot to save

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube. \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
While this may sometimes yield a calibrated link, this is not always the case.
In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
\citet{wang2020weston} apply the embedding framework to understand the Weston-Watkins hinge loss for ordered partitions.

@@

The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
\end{equation}
They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\ref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.

@@

\btw{Yutong's paper commented out here}
%\subsection{Embedding Ordered Partitions}
%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
%
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
%\begin{align*}
%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
%\end{align*}
%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
%
%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
%\begin{equation}\label{eq:ww-hinge}
%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
%\end{equation}
%
%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
%
%\begin{figure}[H]
%		\centering
%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
%	\label{fig:ordered-partition}
%\end{figure}

>>>>

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube. \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
While this may sometimes yield a calibrated link, this is not always the case.
In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.

@@

The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
\end{equation}
They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\eqref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.

@@

\btw{Yutong's paper commented out here; mentioned at beginning of section- June 1 21}
%\subsection{Embedding Ordered Partitions}
%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
%
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
%\begin{align*}
%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
%\end{align*}
%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
%
%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
%\begin{equation}\label{eq:ww-hinge}
%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
%\end{equation}
%
%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
%
%\begin{figure}[H]
%		\centering
%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
%	\label{fig:ordered-partition}
%\end{figure}
